Preregistration analysis, Cost 2 study

### 2019-05-12 Cost2/Cost2_prereg.Rmd
added plots to examine pre/post and order effects

``` {r 16.3.2. Plot Pre/Post reward x handling, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
# pre
t1 <- dataAll %>%
  filter(Choice < 2, Half == "Half_1") %>%
  group_by(SubjID) %>%
  filter(Handling == 10) %>%
  group_by(SubjID, Cost, Reward) %>%
  summarise(pAccept = mean(Choice)) %>%
  group_by(Cost, Reward) %>%
  summarise(propAccept = mean(pAccept),
            SE = sd(pAccept) / sqrt(nSubjs)) %>%
  ungroup() %>%
  mutate(Reward = ifelse(Reward == 20, 12, Reward)) %>%
  ggplot(aes(Reward, propAccept, color = Cost)) +
    geom_point(size = 3, show.legend = F) +
    geom_line(show.legend = F) +
    scale_color_manual(values = cols) +
    scale_fill_manual(values = cols) +
    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
    scale_y_continuous(limits = c(-0.1, 1.1), breaks = c(0, 0.5, 1)) +
    scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
    labs(y = "Proportion Accepted", title = "First Half") +
    theme(legend.key = element_blank(),
          legend.position = c(0.8, 0.25),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))

@@

\bigskip
\bigskip
\bigskip
\bigskip
\bigskip

``` {r Testing grounds, echo=FALSE,fig.align="center",fig.width=10,fig.height=8}
# cond <- as.character(unique(summaryData$Group))
# 
# i <- 1
# test <- allProp2[allProp2$Group == cond[i], ]
# test2 <- trueProp[trueProp$Group == cond[i], ]
# t1 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
#   geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
#   geom_point(size=3, color = cols[i]) +
#   geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
#   labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
#   theme_classic()
# 
# i <- 2
# test <- allProp2[allProp2$Group == cond[i], ]
# test2 <- trueProp[trueProp$Group == cond[i], ]
# t2 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
#   geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
#   geom_point(size=3, color = cols[i]) +
#   geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
#   labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
#   theme_classic()
# 
# i <- 3
# test <- allProp2[allProp2$Group == cond[i], ]
# test2 <- trueProp[trueProp$Group == cond[i], ]
# t3 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
#   geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
#   geom_point(size=3, color = cols[i]) +
#   geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
#   labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
#   theme_classic()
# 
# i <- 4
# test <- allProp2[allProp2$Group == cond[i], ]
# test2 <- trueProp[trueProp$Group == cond[i], ]
# t4 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
#   geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
#   geom_point(size=3, color = cols[i]) +
#   geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
#   labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
#   theme_classic()
# 
# 
# grid.arrange(t1,t3,t2,t4, ncol = 2)

>>>>

``` {r 16.3.2. Plot Pre/Post reward x handling, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
# pre
t1 <- dataAll %>%
  filter(Choice < 2, Half == "Half_1") %>%
  group_by(SubjID) %>%
  filter(Handling == 10) %>%
  group_by(SubjID, Cost, Reward) %>%
  summarise(pAccept = mean(Choice)) %>%
  group_by(Cost, Reward) %>%
  summarise(propAccept = mean(pAccept),
            SE = sd(pAccept) / sqrt(nSubjs)) %>%
  ungroup() %>%
  mutate(Reward = ifelse(Reward == 20, 12, Reward)) %>%
  ggplot(aes(Reward, propAccept, color = Cost)) +
    geom_point(size = 3, show.legend = F) +
    geom_line(show.legend = F) +
    scale_color_manual(values = cols) +
    scale_fill_manual(values = cols) +
    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
    scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
    scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
    labs(y = "Proportion Accepted", title = "First Half") +
    theme(legend.key = element_blank(),
          legend.position = c(0.8, 0.25),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))

@@

### Testing grounds

``` {r Testing plots, echo=FALSE,fig.align="center",fig.width=10,fig.height=8}
# a facet grid of p(acceptances) as a function of reward x handling, distinguishing between first handling time experienced,
# for each cost separately.
# think of doing it for the block order and then prop accepted across costs
dataAll %>%
  group_by(SubjID) %>%
  mutate(BlockOrder = case_when(
    Handling[1] == 2 ~ "Two",
    Handling[1] == 10 ~ "Ten",
    Handling[1] == 14 ~ "Fourteen",
  )) %>%
  group_by(SubjID, Cost, Handling, Reward, BlockOrder) %>%
  summarise(pAccept = mean(Choice)) %>%
  ggplot(aes(interaction(Reward, Handling), pAccept, linetype = BlockOrder, color = BlockOrder)) + 
    geom_point(size = 3) + 
    #geom_errorbar(aes(ymin = meanComplete - SE, ymax = meanComplete + SE), width = 0.2, size = 1) +
    geom_line(aes(group = interaction(Handling, SubjID)), size = 1) +
    #geom_point(aes(y = round(optimal)), shape = 21, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
    labs(x = "Reward.Handling", y = "Proportion Accepted") +
    scale_color_manual(values = cols) +
    facet_wrap(vars(Cost), ncol = 2) +
    theme(legend.key = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))

# now for each first block experienced, how do costs compare per reward x handling
dataAll %>%
  group_by(SubjID) %>%
  mutate(FirstBlock = case_when(
    Handling[1] == 2 ~ "Two",
    Handling[1] == 10 ~ "Ten",
    Handling[1] == 14 ~ "Fourteen",
  )) %>%
  group_by(Cost, Handling, Reward, FirstBlock) %>%
  summarise(pAccept = mean(Choice),
            SE = sd(Choice) / sqrt(length(Choice))) %>%
  ggplot(aes(interaction(Reward, Handling), pAccept, color = Cost)) + 
    geom_point(size = 3) + 
    geom_errorbar(aes(ymin = pAccept - SE, ymax = pAccept + SE), width = 0.4, size = 1) +
    geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
    labs(x = "Reward.Handling", y = "Proportion Accepted") +
    scale_color_manual(values = cols) +
    facet_wrap(vars(FirstBlock), ncol = 3) +
    theme(legend.key = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))
```
